Hydra Battles and Cie

### 2021-08-23 doc/part-hydras.tex
moving to Alectryon: chapter 5 completed

\begin{Coqsrc}
Theorem KS_thm_2_4 (lambda : T1) :
   nf lambda ->
   limitb lambda  ->
   forall i j, (i < j)%nat ->
               const_pathS 0 (canon lambda (S j))
                             (canon lambda (S i)).
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma Lemma2_6_1 (alpha : T1) :  
  nf alpha -> forall beta,  beta t1< alpha  ->
  {n:nat | const_pathS n alpha beta}.
Proof.
  transfinite_induction alpha.
  (* ... *)
\end{Coqsrc}

Intuitively, lemma   \texttt{L2\_6\_1}  shows that if $\beta<\alpha<\epsilon_0$, then there exists  a battle from $\iota(\alpha)$ to $\iota(\beta)$ where the replication factor is constant, although large enough.

@@

%%% traduire la v.f.  (voir %%% A traduire %%%% )

@@

\begin{Coqsrc}
(* Lemma 1 page 300 of [KS] *)

Lemma constant_to_standard_path 
  (alpha beta : T1) (i : nat):
  nf alpha -> const_pathS i alpha beta -> zero  t1< alpha ->
  {l:nat | standard_path (S i) alpha j beta}.
\end{Coqsrc}

@@

\begin{Coqsrc}
Fixpoint standard_gnaw (i:nat)(alpha : T1)(l:nat):  T1  :=
  match l with
  | 0 => alpha
  | S m => standard_gnaw (S i) (canon alpha i) m
  end.
\end{Coqsrc}

\begin{Coqsrc}
  Compute standard_gnaw 2 omega 15.
(*   = zero
     : T1 *)
Compute pp (standard_gnaw 2 (omega^omega)  10).
(*
= (omega + 7)%pT1
     : ppT1
*)
Compute pp (standard_gnaw 4 (omega^omega)  100).
(*
 = (omega ^ 3 * 4 + omega ^ 2 * 5 + omega * 3 + 39)%pT1
     : ppT1 *)
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma standard_path_to_zero :
  forall  alpha i, nf alpha ->
                   {j: nat | standard_path (S i) alpha j zero}.
\end{Coqsrc}

\paragraph*{}
Noq, let us consider two ordinals  $\beta<\alpha<\epsilon_0$.  Let $p$  be some $(n+1)$-path from $\alpha$ to $\beta$.

\begin{Coqsrc}
 Section Constant_to_standard_Proof.

  Variables (alpha beta: T1) (n : nat).
  Hypotheses (Halpha: nf alpha) (Hpos : zero t1<  beta)
             (p : const_pathS n alpha  beta).
\end{Coqsrc}

@@

\begin{Coqsrc}
 Lemma constant_to_standard_0 : 
    {l : nat | standard_fun (S n) alpha l = beta}.
 (* ... *)

End Constant_to_standard_Proof.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma constant_to_standard_path 
  (alpha beta : T1) (i : nat):
  nf alpha -> const_pathS i alpha beta -> zero  t1< alpha ->
  {j:nat | standard_path (S i) alpha j beta}.
\end{Coqsrc}

@@

\begin{Coqsrc}
Corollary  LT_to_standard_path  (alpha beta : T1) :
  beta t1< alpha ->
  {n : nat & {j:nat | standard_path (S n) alpha j beta}}.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma LT_to_standard_battle :
    forall alpha beta,
      beta t1< alpha ->
      exists n i,  battle standard  n (iota alpha) i (iota beta).
\end{Coqsrc}

@@

\begin{Coqsrc}
Section Impossibility_Proof.

Context (mu: T1)
          (Hmu: nf mu)
          (m : Hydra -> T1)
          (Var : Hvariant  T1_wf standard m)
          (Hy : BoundedVariant Var mu).
 \end{Coqsrc}

@@

\begin{Coqsrc}
 Lemma m_ge : m big_h t1<= m small_h.
\end{Coqsrc}

@@

\begin{Coqsrc}
  Lemma m_lt : m small_h  t1< m big_h.

  Theorem Impossibility_std: False.

End Impossibility_Proof.
\end{Coqsrc}

@@

>>>>

\input{movies/snippets/Paths/KSThm24}

@@

\input{movies/snippets/Paths/Lemma261}

Intuitively, lemma   \texttt{Lemma2\_6\_1}  shows that if $\beta<\alpha<\epsilon_0$, then there exists  a battle from $\iota(\alpha)$ to $\iota(\beta)$ where the replication factor is constant, although large enough.

@@

@@

\input{movies/snippets/Paths/constantToStandard}

@@

\input{movies/snippets/Paths/standardGnaw}

@@

\input{movies/snippets/Paths/standardPathToZero}

\paragraph*{}
Now, let us consider two ordinals  $\beta<\alpha<\epsilon_0$.  Let $p$  be some $(n+1)$-path from $\alpha$ to $\beta$.

\input{movies/snippets/Paths/ConstantToStandardProof}

@@

\input{movies/snippets/Paths/constantToStandard0}

@@

\input{movies/snippets/Paths/constantToStandardPath}

@@

\input{movies/snippets/Paths/LTToStandardPath}

@@

\input{movies/snippets/Epsilon0_Needed_Std/LTToStandardBattle}

@@

\input{movies/snippets/Epsilon0_Needed_Std/theContext}

@@

\input{movies/snippets/Epsilon0_Needed_Std/mGe}

@@

\input{movies/snippets/Epsilon0_Needed_Std/mLt}

@@

\input{movies/snippets/Epsilon0_Needed_Std/endOfProof}
